---
title: "Create a Report Server Application"
output: rmarkdown::html_vignette
description: >
  Learn how to create a Report Server Application.
vignette: >
  %\VignetteIndexEntry{Create a Report Server Application}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Workflow

Creating a Thrive Application involves writing a small HTTP server hosted by you. The first step is to create an Application on Thrive so that you can obtain credentials for installing.

## thriver

You can require the thriver library and set your credentials
```{r}
library(thriver)
```

This will provided you with the tools you will need to communicate with the server.
See the [README.md](https://github.com/insilica/thriver#readme) for getting started with the library. Your application devkey will be your thrive api key

## plumber server template
You can run the server.R code which has a simple POST URL. Replace your code with that in the print(json) section.

```{r}
library(plumber)
plumber::pr(here::here("vignettes/server.R")) |>
  plumber::pr_run(port=8001,host="0.0.0.0")
```

In server.R you will see a single route for **/thrive/webhook**. Your application should respond to events sent from the Thrive server to this url. The events your application will receive include "new-file", "new-patient", and "edit-patient". The most pertinent event for report-generating services is the "new-file" event. Some sample code:

```{r}
post_report <- function(patient_id) {
  resp <- get_patient_file_list(patient_id)
  files <- resp$content$data$Patient$files
  # ... do something with files here
  # post_file(patient_id,generate_report(files))
}

```


